Physcraper: A Python package for continually updated gene trees

### 2020-05-11 phylota-overview.Rmd
more phylota examples

1. As an example study of very large and comprehensive phylogeny from minedDNA sequence data, (even if no phylogeny was published there, only the method to do so):
  - @beaulieu2012modeling
  -

1. As an example tool that mines GenBak data for phylogenetic reconstruction:
  - original publication of PHLAWD [@smith2009mega]
  -

1. When the software was actually used to construct a DNA data set for phylogenetic reconstruction of:
  - A 1000 tip phylogeny of the family of the nightshades [@sarkinen2013solanaceae]
  - A 56 tip phylogeny of crustacean zooplancton [@helmus2010communities] -- ecological study
  - A 63 tip phylogeny of the Salmonidae family [@crete2012salmonidae]
  - A 321 tip phylogeny of Testudines [@thomson2010sparse]

1. When the website was used to identify sequences and markers available in
GenBank for a particular group, In this cases, the dataset mining was performed with other tools, or not performed at all and just used for discussion:
  - A 812 tips phylogeny of the Order Chiroptera [@shi2015speciation] -- dataset constructed with PHLAWD
  - A 1276 tips phylogeny of the Fabaceae [@legume2013legume] -- dataset constructed by hand (I think??)
  - A review of dated phylogenies of fire-prone tropical savanna species from Brazil [@simon2012cerrado] -- just for discussion of the lack of markers available for these species on GenBank

>>>>

1. As an example study of very large and comprehensive phylogeny from mined DNA sequence data, (even if no phylogeny was really published there, only the method to do so):
  - @beaulieu2012modeling
  -

1. As an example of a tool that mines GenBank data for phylogenetic reconstruction:
  - original publication of PHLAWD [@smith2009mega]
  - an analysis identifying research priorities and data requirements for resolving
  the red algal tree of life [@verbruggen2010data]
  - a review for ecologists about phylogenetic tools [@roquet2013building]

1. When the software was actually used to construct (partially or in full) a DNA
data set to be used for phylogenetic reconstruction:
  - A 1000 tip phylogeny of the family of the nightshades [@sarkinen2013solanaceae]
  - A 56 tip phylogeny of crustacean zooplancton [@helmus2010communities] -- ecological study
  - A 63 tip phylogeny of the Salmonidae family [@crete2012salmonidae]
  - A 321 tip phylogeny of Testudines [@thomson2010sparse]
  - A 69 taxa phylogeny of the family Cyprinodontidae of the pupfish [@martin2011trophic]
  - A 2,957 taxa phylogeny of the class Moniloformopses of living ferns [@lehtonen2011towards]
  - A 2,573 species phylogeny of the Papilionoidea [@hardy2014specialization]
  - A 23 taxa phylogeny of the California flora [@anacker2011origins]
  - Phylogenies of 6 different clades of flowering plants representing an independent
  evolutionary origin of extrafloral nectaries: *Byttneria* (Malvaceae), *Pleopeltis* (Polypodiaceae),
  *Polygoneae* (Polygoneaceae), *Senna* (Fabaceae), *Turnera* (Passifloraceae), and *Viburnum*
  (Adoxaceae) [@weber2014defense].
  - To supplement DNA data sets of various pre-existing mammalian phylogenetic trees
  sampled at different taxonomic levels [@faurby2015species]
  -

1. When the website was used to identify sequences and markers available in
GenBank for a particular group. In this cases, the dataset mining was either performed
with other tools, or not performed at all and just used for discussion:
  - A 812 tips phylogeny of the Order Chiroptera [@shi2015speciation] -- dataset
  constructed with PHLAWD
  - A 1276 tips phylogeny of the Fabaceae [@legume2013legume] -- dataset constructed
  by hand (I think??)
  - A review of dated phylogenies of fire-prone tropical savanna species from Brazil
  [@simon2012cerrado] -- just for discussion of the lack of markers available for
  these species on GenBank
  - A review of the phylogeetic sof the Apicomplexa, a parasitic phylum on unicellular
  protists [@morrison2009apicomplexa].
  - Three  data sets from phylota (the suborder Pleurodira of side-necked turtles;
    the family Cactaceae of cacti; and the Amorpheae, a clade of legumes) were used
    to demonstrate and exemplify phylogenetic decisiveness [@sanderson2010phylogenomics]
